Tropical Andes plant trait data TRY

### 2023-10-25 code/L0/L0_TropicalAndes_plants_GIFT.Rmd
update to include plant growth form

# Retrive GIFT data
```{r}
trait_meta <- GIFT_traits_meta()
```
Traits of interest: plant height (ID = 1.6.3), lifespan (ID = 2.2.1), dispersal syndrome (ID = 3.3), Plant_height_min (1.6.1), Plant_height_max (1.6.2), Fruit_type_1 (3.16.1), fruit_dryness_1 (3.18.1), Fruit_length_min (3.13.1), Fruit_length_max (3.13.2), Fruit_length_mean (3.13.3), Seed_mass_min (3.2.1), Seed_mass_max (3.2.2), Seed_mass_mean (3.2.3), Seed_length_min (3.10.1), Seed_length_max (3.10.2), Seed_length_mean (3.10.3), Seed_width_min (3.11.1), Seed_width_max (3.11.2), Seed_width_mean (3.11.3)

@@

seed_width_mean <- GIFT_traits(trait_IDs = c("3.11.3"))
seed_width_min <- GIFT_traits(trait_IDs = c("3.11.1"))
seed_width_max <- GIFT_traits(trait_IDs = c("3.11.2"))
```

@@

seed_width_mean <- seed_width_mean %>% rename(trait_value = trait_value_3.11.3, species = work_species)
seed_width_min <- seed_width_min %>% rename(trait_value = trait_value_3.11.1, species = work_species)
seed_width_max <- seed_width_max %>% rename(trait_value = trait_value_3.11.2, species = work_species)
```

@@

seed_width_mean <- seed_width_mean %>% select(species, trait_value)
seed_width_min <- seed_width_min %>% select(species, trait_value)
seed_width_max <- seed_width_max %>% select(species, trait_value)
```

```{r}
# add trait name column
height_mean$trait_name <- "plant_height"
height_min$trait_name <- "plant_height_min"
height_max$trait_name <- "plant_height_max"
lifespan$trait_name <- "plant_lifespan"
dispersal_syndrome_1$trait_name <- "dispersal_syndrome_1"
dispersal_syndrome_2$trait_name <- "dispersal_syndrome_2"
fruit_type$trait_name <- "fruit_type"
fruit_dryness$trait_name <- "fruit_dryness"
fruit_length_mean$trait_name <- "fruit_length_mean"
fruit_length_min$trait_name <- "fruit_length_min"
fruit_length_max$trait_name <- "fruit_length_max"
seed_mass_mean$trait_name <- "seed_mass_mean"
seed_mass_min$trait_name <- "seed_mass_min"
seed_mass_max$trait_name <- "seed_mass_max"
seed_length_mean$trait_name <- "seed_length_mean"
seed_length_min$trait_name <- "seed_length_min"
seed_length_max$trait_name <- "seed_length_max"
seed_width_mean$trait_name <- "seed_width_mean"
seed_width_min$trait_name <- "seed_width_min"
seed_width_max$trait_name <- "seed_width_max"

```

@@

```{r}
#combine all trait dataframes into one long table
GIFT_traits <- dplyr::bind_rows(height_mean, height_min, height_max, lifespan, dispersal_syndrome_1, dispersal_syndrome_2, fruit_type, fruit_dryness, fruit_length_mean, fruit_length_min, fruit_length_max, seed_mass_mean, seed_mass_min, seed_mass_max, seed_length_mean, seed_length_min, seed_length_max, seed_width_mean, seed_width_min, seed_width_max)
```

>>>>

# Retrive GIFT data
```{r}
GIFT_traits_meta()
```
Traits of interest: plant height (ID = 1.6.3), lifespan (ID = 2.2.1), dispersal syndrome (ID = 3.3), Plant_height_min (1.6.1), Plant_height_max (1.6.2), Fruit_type_1 (3.16.1), fruit_dryness_1 (3.18.1), Fruit_length_min (3.13.1), Fruit_length_max (3.13.2), Fruit_length_mean (3.13.3), Seed_mass_min (3.2.1), Seed_mass_max (3.2.2), Seed_mass_mean (3.2.3), Seed_length_min (3.10.1), Seed_length_max (3.10.2), Seed_length_mean (3.10.3), Seed_width_min (3.11.1), Seed_width_max (3.11.2), Seed_width_mean (3.11.3), Growth_form (1.2.1)

@@

seed_width_mean <- GIFT_traits(trait_IDs = c("3.11.3"))
seed_width_min <- GIFT_traits(trait_IDs = c("3.11.1"))
seed_width_max <- GIFT_traits(trait_IDs = c("3.11.2"))

growth_form <- GIFT_traits(trait_IDs = c("1.2.1"))
```

@@

seed_width_mean <- seed_width_mean %>% rename(trait_value = trait_value_3.11.3, species = work_species)
seed_width_min <- seed_width_min %>% rename(trait_value = trait_value_3.11.1, species = work_species)
seed_width_max <- seed_width_max %>% rename(trait_value = trait_value_3.11.2, species = work_species)

growth_form <- growth_form %>% rename(trait_value = trait_value_1.2.1, species = work_species)
```

@@

seed_width_mean <- seed_width_mean %>% select(species, trait_value)
seed_width_min <- seed_width_min %>% select(species, trait_value)
seed_width_max <- seed_width_max %>% select(species, trait_value)

growth_form <- growth_form %>% select(species, trait_value)
```

```{r}
# add trait name column
height_mean$trait_name <- "plant_height"
height_min$trait_name <- "plant_height_min"
height_max$trait_name <- "plant_height_max"
lifespan$trait_name <- "plant_lifespan"
dispersal_syndrome_1$trait_name <- "dispersal_syndrome_1"
dispersal_syndrome_2$trait_name <- "dispersal_syndrome_2"
fruit_type$trait_name <- "fruit_type"
fruit_dryness$trait_name <- "fruit_dryness"
fruit_length_mean$trait_name <- "fruit_length_mean"
fruit_length_min$trait_name <- "fruit_length_min"
fruit_length_max$trait_name <- "fruit_length_max"
seed_mass_mean$trait_name <- "seed_mass_mean"
seed_mass_min$trait_name <- "seed_mass_min"
seed_mass_max$trait_name <- "seed_mass_max"
seed_length_mean$trait_name <- "seed_length_mean"
seed_length_min$trait_name <- "seed_length_min"
seed_length_max$trait_name <- "seed_length_max"
seed_width_mean$trait_name <- "seed_width_mean"
seed_width_min$trait_name <- "seed_width_min"
seed_width_max$trait_name <- "seed_width_max"
growth_form$trait_name <- "growth_form"
```

@@

```{r}
#combine all trait dataframes into one long table
GIFT_traits <- dplyr::bind_rows(height_mean, height_min, height_max, lifespan, dispersal_syndrome_1, dispersal_syndrome_2, fruit_type, fruit_dryness, fruit_length_mean, fruit_length_min, fruit_length_max, seed_mass_mean, seed_mass_min, seed_mass_max, seed_length_mean, seed_length_min, seed_length_max, seed_width_mean, seed_width_min, seed_width_max, growth_form)
```

### 2023-10-25 code/L0/L0_TropicalAndes_plants_TRY.Rmd
update to include plant growth form

# Load TRY data
Data was obtained from https://www.try-db.org/TryWeb/Prop0.php 
```{r}
try_data <- rtry_import("G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0/TRY/28165_02082023081407/28165.txt")
```

```{r}
glimpse(try_data)
```

#Subset to species list
```{r}
species_list <- read.csv("G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L1/TropicalAndes_plant_Forest_SpeciesList.csv")
species_list <- species_list$x
```

```{r}
try_data_filtered <- try_data %>%
  filter(AccSpeciesName %in% species_list)
```

# Summary 
```{r}
glimpse(try_data_filtered)
```

```{r}
print("The number of records is")
nrow(try_data_filtered)
print("The number of species is" )
length(unique(try_data_filtered$AccSpeciesName))
```

```{r}
try_data_filtered %>% count(TraitName)
```

# Write data to csv
```{r}
TropicalAndes_TRY_path <- file.path(output_path,"TropicalAndes_TRY_plant_traits_forestSpecies.csv") 
write.csv(try_data_filtered, file = TropicalAndes_TRY_path)
```

>>>>

# Load TRY data
Data was obtained from https://www.try-db.org/TryWeb/Prop0.php 
```{r}
try_data <- rtry_import("G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0/TRY/29548_24102023041242/29548.txt")
```

# Summary
```{r}
glimpse(try_data)
```

```{r}
print("The number of records is")
nrow(try_data)
print("The number of species is" )
length(unique(try_data$AccSpeciesName))
```

```{r}
try_data %>% count(TraitName)
```

# Write data to csv
```{r}
write.csv(try_data, file = file.path(output_path,"TropicalAndes_TRY_plant_traits.csv") )
```
